Dynamics of Global and Local Social Influence

### 2021-09-01 manuscript_global_local_influence.Rmd
Fixed footnote

The explanatory variables are two measures we construct to represent the local and global prevalence of the behavior in question. The local score is the average behavior among ego’s friends. Thus, if ego has five nominated friends and two of them drink, then ego’s local score at that wave would be $\frac{2}{5}$. Local score, then, varies across respondents, reflecting differences in their immediate friendship networks. The global score, in turn, is the same for all individuals embedded in the same structure at a given wave. We calculate it by looking at the average behavior of the most popular nodes at a given time. To operationalize this idea of popularity, we look at eigen-vector centrality. We consider the nodes to be among the most popular if they have an eigen-vector centrality score above the 85th percentile[^There are different ways of operationalizing popularity; cf. [@robalinoPeerEffectsAdolescent2018]][^We conducted the same analyses using the 80th and 90th percentile as cutoffs and got largely consistent results]. Here, we decide
to use a threshold that indexes a group of high-status, popular nodes. This captures how social learning scholars have discussed and formalized prestige-biased social learning [@jimenezPrestigebiasedSocialLearning2019]. We want to reflect the idea that, when using this social learning strategy, agents look at a few individuals who they consider to be successful. Therefore, having a threshold that helps us distinguish between this group and the rest of the nodes is appropriate. Say then that, in a given school, there are six nodes whose eigen-vector centrality is above that threshold, and one of them drinks. The global score for all nodes in that network in that wave would be $\frac{1}{6}$. Though these constructed variables are necessarily rough approximations, we consider that these scores can help us disentangle the importance of global and local sources of influence for different behaviors.

>>>>

The explanatory variables are two measures we construct to represent the local and global prevalence of the behavior in question. The local score is the average behavior among ego’s friends. Thus, if ego has five nominated friends and two of them drink, then ego’s local score at that wave would be $\frac{2}{5}$. Local score, then, varies across respondents, reflecting differences in their immediate friendship networks. The global score, in turn, is the same for all individuals embedded in the same structure at a given wave. We calculate it by looking at the average behavior of the most popular nodes at a given time. To operationalize this idea of popularity, we look at eigen-vector centrality. We consider the nodes to be among the most popular if they have an eigen-vector centrality score above the 85th percentile.^[There are different ways of operationalizing popularity; cf. [@robalinoPeerEffectsAdolescent2018]]. Here, we decide
to use a threshold that indexes a group of high-status, popular nodes.^[We conducted the same analyses using the 80th and 90th percentile as cutoffs and got largely consistent results] This captures how social learning scholars have discussed and formalized prestige-biased social learning [@jimenezPrestigebiasedSocialLearning2019]. We want to reflect the idea that, when using this social learning strategy, agents look at a few individuals who they consider to be successful. Therefore, having a threshold that helps us distinguish between this group and the rest of the nodes is appropriate. Say then that, in a given school, there are six nodes whose eigen-vector centrality is above that threshold, and one of them drinks. The global score for all nodes in that network in that wave would be $\frac{1}{6}$. Though these constructed variables are necessarily rough approximations, we consider that these scores can help us disentangle the importance of global and local sources of influence for different behaviors.
